%
% File:   test3.tex
% Date:   17-Jul-12
% Author: I. Chuang <ichuang@mit.edu>
%
% Example latex source file for an edX course.
% This file can be compiled using
%
%   python latex2edx -prefix ATEST test3.tex
%
% to generate all the content files for an example edX course named
% "1.00x".  The files are saved in a subdirectory named "1.00x", and
% include:
%
%     1.00x/course.xml               - main table of contents for course
%     1.00x/problem/Problem_1.xml   - problem 1 (symbolic response example)
%     1.00x/problem/Problem_2.xml   - problem 2 (option response example)

\documentclass[12pt]{article}

\usepackage{edXpsl}	% edX

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{edXcourse}{1.00x}{1.00x Fall 2012}

\begin{edXchapter}{Unit 1}

\begin{edXsection}{Introduction}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{edXproblem}{Problem 1}{40}

\section{Example of symbolic response}  
 
This is a sample problem, which is worth 40 points.  What is the number made famous by
Hitchhiker's guide to the galaxy?

\edXabox{type='symbolic' size='90' expect='42' }

\end{edXproblem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{edXproblem}{Problem 2}{10}

\section{Example of option response}  

This is a sample problem, which is worth 10 points.

Give the correct python {\tt type} for the following expressions.  Select {\tt noneType} if the expression is illegal.

\begin{itemize}
\item {\tt 3}   \edXabox{expect="int" options="noneType","int","float"}
\item {\tt 5.2} \edXabox{expect="float" options="noneType","int","float"}
\item {\tt 3/2} \edXabox{expect="int" options="noneType","int","float"}
\item {\tt 1+[]} \edXabox{expect="noneType" options="noneType","int","float"}
\end{itemize}

\end{edXproblem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{edXproblem}{Problem 3}{10}

\section{Example of string response}  

What state is Detroit in?

\edXabox{expect="Michigan" type="string"}

\end{edXproblem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{edXvertical}{A sample vertical - multiple problems in one day}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{edXproblem}{Problem 3.5}{10}

\section{Example of numerical response}  

What is the numerical value of $pi$?

\edXabox{expect="3.14159" type="numerical" tolerance='0.01' }

\end{edXproblem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{edXproblem}{Problem 4}{10}

\section{Example of custom response}  

This problem demonstrates the use of a custom python script used for
checking the answer.

\begin{edXscript}
def sumtest(expect,ans):
    (a1,a2) = map(float,eval(ans))
    return (a1+a2)==10
\end{edXscript}

Enter a python list of two numbers which sum to 10:

\edXabox{expect="[1,9]" type="custom" cfn="sumtest"}

\end{edXproblem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{edXvertical}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{edXproblem}{Problem 4}{10}

\section{Example of external response (coding problem)}  

This problem demonstrates a python coding problem.

\begin{edXscript}
initial_display = ""
answer = """
print "hello world"
"""
preamble = """ 
code = '''
"""
test_program = """
'''
code = code.replace('print ','print >> LOG_OUTPUT, ')
exec(code)
"""
\end{edXscript}

Write python code which prints out ``hello world''

\edXabox{type="external" tests="1"}

\end{edXproblem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{edXsection}
\end{edXchapter}
\end{edXcourse}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
