\documentclass[12pt]{article}

\usepackage{edXpsl}	% edX

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{edXcourse}{edx4edx}{edx4edx}

\begin{edXchapter}{Author tools}

\begin{edXsection}{Sample problems generated from LaTeX}

\begin{edXsequential}

\begin{edXproblem}{Example inline textinput answer box}{40}

\section{Inline Answer Box Test}  

\begin{edXscript}

def dumtest(expect,ans):
    return True

\end{edXscript}

Clifford gates and measurements are not the only components of quantum
circuits. In fact, if they were, quantum computers not be more
powerful than classical ones! Here we consider some unitary and
non-unitary operations that take quantum states to other valid states.

\subsection{Rotations}

Recall the Bloch vector $[a,b,c]$ for a single qubit state $\rho$ is defined so that 
\begin{equation}
\rho = \frac12(I+aX+bY+cZ)
\end{equation}
where $I$ is the $2\times2$ identity matrix and $X,Y,$ and $Z$ are the
Pauli matrices. The purity of state $\tau$ for $n$-qubits is the trace
of $\tau^2$, a quantity which is always between $1/2^n$ and $1$, with
$1$ being pure and $1/2^n$ being completely mixed. What is the
condition on $a,b,$ and $c$ such that $\rho$ is a pure state? Enter
you answer as a single expression that will be 0 if (and only if)
$\rho$ is pure. For example, $(4-a+b+c^4)$ is syntactically correct
but $(4-a+b+c^4)=0$ is not.


\edXinline{$\rho$ is pure iff $0=$ } \edXabox{inline='1' type="custom" cfn='dumtest' expect="a^2 + b^2 + c^2 - 1"}

All single qubit unitary operations can be expressed, up to a global
phase, as a rotation about an axis in Bloch sphere space. If the axis
is $\hat n=[n_x,n_y,n_z]$ (a unit vector) and the rotation angle is
$\theta$, then the rotation may be written in terms of the Pauli
matrices as
\begin{equation}
U=e^{i\theta\left(n_x X+n_y Y+n_z Z\right)}.
\end{equation}

\end{edXproblem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{edXsequential}

\end{edXsection}
\end{edXchapter}
\end{edXcourse}

\end{document}